Capstone Movielens Report

### 2025-01-27 reports/capstone-movielens-report.Rmd
Report updated!

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

## R Markdown

@@

## Including Plots

@@

>>>>

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
output:
  html_document: 
    fig_caption: true
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
---

@@

## Introduction / Overview / Executive Summary

@@

## Methods / Analysis

@@

## Conclusion

Hello Conclusion!

This is a great conclusion, isn't is?!!
